---
title: "Task 19"
author: "Hayden Armour"
date: "11/14/2022"
output: 
  html_document:
    keep_md: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load in libraries 
```{r}
library(tidyverse)
library(maps)
library(USAboundaries)
library(leaflet)
```


```{r}
statesmap <- sf::st_as_sf(map("state", plot = FALSE, fill = TRUE))
```

Create dataframe for the cities data
```{r}
cities <- us_cities() 
  
head(cities)
```

Create dataframe for the states data
```{r}
states <- us_states()

head(states)
```

Create dataframe for the county data
```{r}
county <- us_counties()

head(county)
```

Gets the county data for Idaho 
```{r}
idahocounties <- us_counties(states = "ID")
```


Filter out Alaska and Hawaii since they are not included in the map we are recreating 
```{r}
filteredcities <- cities %>%
  filter(state_name != 'Alaska', state_name != 'Hawaii')
```

Group the new dataset by state, and since we are looking for the 3 largest cities, we will arrange them by population from greatest to least
```{r}
top3cities <- filteredcities %>%
  group_by(state_name) %>%
  arrange(desc(population))

head(top3cities)
```

Take the top 3 largest population cities in each state 
```{r}
threelargestcities <- top3cities %>%
  slice(1:3)

head(threelargestcities)
```

Create datasets that hold the largest, the middle, and the smallest populations for each state in the U.S.
```{r}
largest <- threelargestcities %>%
  slice(1:1)
middle <- threelargestcities %>%
  slice(2:2)
smallest <- threelargestcities %>%
  slice(3:3)

head(largest)

largestcity <- largest %>%
  select(city)
```


```{r}
plot1 <- leaflet() %>% 
  addTiles() %>%
  addPolygons(data = statesmap, fillColor = 'white', weight = 1, color = 'grey') %>%
  addPolygons(data = idahocounties, fillColor = 'white', , weight = 1, color = 'grey') %>%
  addCircleMarkers(data = smallest, radius = 1, color = 'skyblue', opacity = 1) %>%
  addCircleMarkers(data = middle, radius = 2, color = 'blue', opacity = 1) %>%
  addCircleMarkers(data = largest, radius = 5, color = 'navy', opacity = 1) %>%
  addCircleMarkers(data = largestcity, label = ~city)

  
  

plot1
```






















