---
title: "Task 11"
author: "Hayden Armour"
date: "10/3/2022"
output: 
  html_document:
    keep_md: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(readr)
library(knitr)
library(tidyverse)
library(dplyr)
library(forcats)
library(downloader)
library(corrplot)
```

```{r}
download.file("https://raw.githubusercontent.com/fivethirtyeight/data/master/fandango/fandango_score_comparison.csv", "fandango")
```

```{r}
movies <- read.csv('fandango')
```

```{r}
head(movies)
str(movies)
```


```{r}
movieratings <- movies %>%
  select(FILM, Fandango_Ratingvalue, RT_norm, Metacritic_norm, IMDB_norm) %>%
  pivot_longer(2:5, names_to = "source", values_to = "score") %>%
  select(FILM, source, score) %>%
  head(n = 40)

movieratings
```


```{r}
movieplot1 <- ggplot(data = movieratings, mapping = aes(x = source, y = score, color = FILM)) +
  geom_col(position = 'dodge') +
  labs(x = "Ratings Source", y = "Average Score", title = "Film Scores Broken Down by Different Sources")

movieplot1
```


First 20 rows of the tidy'd table   
```{r}
head(movieratings, n = 20)
```

I had to narrow the data down to only 20 rows because the entire data set makes my computer crash when creating a grahhic. From what we can see, Fandango_Ratingvalue has, overall, the highest scores, followed by RT_norm, then IMBD_norm and then Metacritic_norm. I used differing colors for FILMS so that it was clear to see how they compared, and the x-axis is broken down by the source of the ratings. Hot Tub Time Machine 2 consistently had the lowest rating. 





























