---
title: "Task 2"
author: "Hayden Armour"
date: "9/4/2022"
output:
  html_document:
    keep_md: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Installing and Loading Packages 
```{r}
library(knitr)
library(tidyverse)
```

#Convert the iris data to a tibble called iris_data.
```{r}
iris_data <- as_tibble(iris)
iris_data
```

#Arrange the iris data by Sepal.Length and display the first ten rows.
```{r}
a.sepal <- arrange(iris_data, Sepal.Length) 
head(a.sepal, 10)
```


#Select the Species and Petal.Width columns and put them into a new data set called testdat.
```{r}
testdat <- select(iris_data, Species, Petal.Width)
testdat
```


#Create a new table called species_mean that has the mean for each variable for each Species.
```{r}
species_mean <- iris_data %>%
  group_by(Species) %>%
  summarise(mean(Sepal.Length), mean(Sepal.Width), mean(Petal.Length), mean(Petal.Width)) 
species_mean

```


#Create a data frame called iris_min with only the observations with at least 3 for Sepal.Width and not 2.5 for Petal.Width.
```{r}
select_iris <- select(iris_data, Species, Sepal.Width, Petal.Width, Sepal.Length, Petal.Length) 
iris_min <-filter(select_iris, Sepal.Width >= 3, Petal.Width != 2.5)

iris_min
```

#Create a data frame called iris_size with a column Sepal.Size which is
```{r}
iris_size <- iris_data %>%
  mutate(Sepal.Size =
           case_when(
             Sepal.Length < 5 ~ "small",
             Sepal.Length >= 5 & Sepal.Length < 6.5 ~ "medium",
             Sepal.Length >= 6.5 ~ "large"))
iris_size
```

#Create a data frame called iris_rank which ranks all of the data by Petal.Length, where a ranking of 1 is the largest Petal.Length and order by ranking.
```{r}
iris_ranking <- arrange(iris_data, desc(Petal.Length)) 
iris_rank <- mutate(iris_ranking, rank=min_rank(Petal.Length))


iris_rank
```

#Read about the ?summarize_all() function and get a new table with the means and standard deviations for each species.
```{r}
speciesmean_speciesstd <- iris_data %>%
  group_by(Species) %>%
  summarise_all(list(Mean=mean, Std_dev = sd)) 
speciesmean_speciesstd
```

#Develop a few novel questions that the data can answer
###Are there certain species of plant that grow larger than others? If so, what is the gap between the largest, and the smallest. 
###Are there more "small" than "large" species of flowers? (based on criteria provided)
###Is the greatest difference in Petal.Length means between setosa and versicolor, setosa and virginica, or versicolor and virginica? 
###Which species has the highest standard deviation? Which has the smallest? 

#Feedback summary 
###Those that were asked to look at the questions beleived that these questions were novel, however, did not interest them. They did not know what a Sepal was, and weren't sure how these different measurements were measured. Once explained, and once ther results were given, they were not surprised by my findings. 






