---
title: "Task 14"
author: "Hayden Armour"
date: "10/17/2022"
output: 
  html_document:
    keep_md: TRUE
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(knitr)
library(tidyverse)
library(downloader)
library(corrplot)
library(stringi)
```

```{r}
download.file("https://github.com/WJC-Data-Science/DTS350/raw/master/bible.csv", "bible")
```

```{r}
bible <- read.csv("bible")

tail(bible)
head(bible)
```

What is the average verse length (number of words) in the Old Testament compared to the New Testament?

Data filtered to include only the old testament 
```{r}
oldtestament <- bible %>%
  filter(volume_title == "Old Testament") %>%
  select(scripture_text)

head(oldtestament)
```

Data filtered to include only the new testament 
```{r}
newtestament <- bible %>%
  filter(volume_title == "New Testament") %>%
  select(scripture_text)

head(newtestament)
```

Function that can be used to find verse length 
```{r}
average_verse_length <- vector("integer", nrow(newtestament))

for (i in seq(1,nrow(newtestament))) {average_verse_length[[i]] <- stri_stats_latex(newtestament$scripture_text[i]) [[4]]
}

mean(average_verse_length)

```
The average verse length in the oldtestament is 26.42074
The average in the newtestament is 22.70517 


How often is the word LORD (case insensitive) in the Old Testament compared to the New Testament?
```{r}

str_count(oldtestament, "(?i)lord")

str_count(newtestament, "(?i)lord")

```
(?i) = case insensitive modifier 
str_count finds how often lord is repeated

Lord appears in the Old Testament 7,273 times
Lord appears in the New Testament 736 times


Visualization
How does the word count distribution by verse look for each book in the New Testament?
```{r}
newtestament1 <- bible %>%
  filter(volume_title == "New Testament") %>%
  select(scripture_text, book_title, verse_number)

head(newtestament1)
```


```{r}
average_verse_lengthgraph <- vector("integer", nrow(newtestament1))

for (i in seq(1,nrow(newtestament1))) {average_verse_lengthgraph[[i]] <- stri_stats_latex(newtestament1$scripture_text[i]) [[4]]
}

average_verse_lengthgraph
```


```{r}
new_avg_length <- bind_cols(newtestament1, average_verse_lengthgraph) %>%
  mutate(word_count = ...4) %>%
  select(book_title, verse_number, word_count)
 
head(new_avg_length)
```


```{r}
ggplot(data = new_avg_length, mapping = aes(x = word_count)) +
  geom_histogram(color = "black", fill = "white") +
  theme_dark() +
  labs(title = "Word Count Distribution by Verse", subtitle = "For Each Book in the New Testament",
       x = "Word Count Distribution", y = "Count") +
  theme(plot.title = element_text(hjust = .5)) +
  theme(plot.subtitle = element_text(hjust = .5)) 
  #stat_bin(geom = "text", aes(label = ..count..), vjust = 1.5, size = 2.5)
```


```{r}
plot1 <- ggplot(data = new_avg_length, mapping = aes(y = word_count, x = verse_number, fill = book_title)) +
  geom_col() +
  facet_wrap(~book_title) +
  labs(title = "Word Count Distribution by Verse", subtitle = "For Each Book in the New Testament",
       x = "Word Count Distribution", y = "Count") +
  theme(plot.title = element_text(hjust = .5)) +
  theme(plot.subtitle = element_text(hjust = .5)) 

plot1
```


```{r}
plot2 <- ggplot(data = new_avg_length, mapping = aes(x = word_count, fill = book_title)) +
  geom_bar(color = 'black') +
  labs(title = "Word Count Distribution by Verse", subtitle = "For Each Book in the New Testament",
       x = "Word Count Distribution", y = "Count") +
  theme(plot.title = element_text(hjust = .5)) +
  theme(plot.subtitle = element_text(hjust = .5)) 

plot2
```


```{r}
plot3 <- ggplot(data = new_avg_length, mapping = aes(x = word_count, y = verse_number, color = book_title)) +
  geom_point() +
  labs(title = "Word Count Distribution by Verse", subtitle = "For Each Book in the New Testament",
       x = "Word Count Distribution", y = "Count") +
  theme(plot.title = element_text(hjust = .5)) +
  theme(plot.subtitle = element_text(hjust = .5)) 

plot3
```


```{r}
plot4 <- ggplot(data = new_avg_length, mapping = aes(x = word_count, y = verse_number, color = book_title)) +
  geom_point() +
  facet_wrap(~book_title) +
  labs(title = "Word Count Distribution by Verse", subtitle = "For Each Book in the New Testament",
       x = "Word Count Distribution", y = "Count") +
  theme(plot.title = element_text(hjust = .5)) +
  theme(plot.subtitle = element_text(hjust = .5)) 

plot4
```


```{r}
plot5 <- ggplot(data = new_avg_length, mapping = aes(x = word_count, fill = book_title)) +
  geom_histogram() +
  labs(title = "Word Count Distribution by Verse", subtitle = "For Each Book in the New Testament",
       x = "Word Count Distribution", y = "Count") +
  theme(plot.title = element_text(hjust = .5)) +
  theme(plot.subtitle = element_text(hjust = .5)) 

plot5
```


























