---
title: "Task 18"
author: "Hayden Armour"
date: "11/7/2022"
output: 
  html_document:
    keep_md: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(remotes)

library(sf)

library(maps)

library(USAboundariesData)

library(USAboundaries)

#install.packages("ggrepel")
library(ggrepel)
#geom_label_repel()

library(ggplot2)
library(readr)
library(knitr)
library(tidyverse)
library(dplyr)
library(forcats)
library(downloader)
library(corrplot)
library(tidyquant)
library(timetk)
library(dygraphs)
```

Create dataframe for the cities data
```{r}
cities <- us_cities() 
  
head(cities)
```

Create dataframe for the states data
```{r}
states <- us_states()

head(states)
```

Create dataframe for the county data
```{r}
county <- us_counties()

head(county)
```

Gets the county data for Idaho 
```{r}
idahocounties <- us_counties(states = "ID")
```

Create the dataframe with the state name and the geometry (the longitutde and latitude)
```{r}
statesmap <- sf::st_as_sf(map("state", plot = FALSE, fill = TRUE))

head(statesmap)
```

Filter out Alaska and Hawaii since they are not included in the map we are recreating 
```{r}
filteredcities <- cities %>%
  filter(state_name != 'Alaska', state_name != 'Hawaii')
```

Group the new dataset by state, and since we are looking for the 3 largest cities, we will arrange them by population from greatest to least
```{r}
top3cities <- filteredcities %>%
  group_by(state_name) %>%
  arrange(desc(population))

head(top3cities)
```

Take the top 3 largest population cities in each state 
```{r}
threelargestcities <- top3cities %>%
  slice(1:3)

head(threelargestcities)
```

Create datasets that hold the largest, the middle, and the smallest populations for each state in the U.S.
```{r}
largest <- threelargestcities %>%
  slice(1:1)
middle <- threelargestcities %>%
  slice(2:2)
smallest <- threelargestcities %>%
  slice(3:3)

head(largest)
```

Create the graphic that we were supposed to recreate
```{r}


ggplot() +
  geom_sf(data = statesmap, fill = NA) +
  geom_sf(data = idahocounties, fill = NA) +
  geom_sf(data = smallest, aes(size = population/1000), color = "lightblue") +
  geom_sf(data = middle, aes(size = population/1000), color = "royalblue1") +
  geom_sf(data = largest, aes(size = population/1000), color = "royalblue4") +
  geom_sf_label(data = largest, aes(label = city), color = "darkblue", nudge_x = 1.5, nudge_y = 1, size = 2) +
  scale_size_continuous(name = 'Population\n(1,000)') +
  labs(title="3 Largest Cities (by Population) Per State", x="Latitude",y="Longitude") +
  theme_bw()
```
Could not figure out how to get geom_label_repel to space the labels out better

















































