---
title: "Case 9"
author: "Hayden Armour"
date: "10/31/2022"
output: 
  html_document:
    keep_md: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(readr)
library(knitr)
library(tidyverse)
library(dplyr)
library(forcats)
library(downloader)
library(corrplot)
library(tidyquant)
library(timetk)
library(dygraphs)
```

Section 1 
```{r}
tickers_today <- tq_get(c("CXW", "F", "GM", "JCP", "KR", "WDC", "NKE","T", "WDAY", "WFC", "WMT"), get = "stock.prices", from = today()-years(5), to = today())

head(tickers_today)

```

Set up to build interactive graph 
```{r}
fiveyearadjusted <- tickers_today %>%
  select(symbol, date, adjusted) %>%
  pivot_wider(names_from = symbol, values_from = adjusted) %>%
  tk_xts(date_var = date)


head(fiveyearadjusted)
```

Graph 1
```{r}
dygraph(fiveyearadjusted, main = "Straw Broom Chart Percent") %>%
  dyRebase(percent = TRUE) %>%
  dyShading(from = today()-years(5), to = today()) %>%
  dyRangeSelector()
```

Graph 2
```{r}
dygraph(fiveyearadjusted, main = "Stock Price Comparison") %>%
  dyHighlight(highlightCircleSize = 2, 
              highlightSeriesBackgroundAlpha = 0.2,
              hideOnMouseOut = FALSE) %>% 
  dyOptions(axisLineColor = "red",
            gridLineColor = "lightblue") %>% 
  dyRangeSelector(dateWindow = c(today()-years(5),today())) 
```


Set up for graph below
```{r}
fiveyearvolume <- tickers_today %>%
  select(symbol, date, volume)

head(fiveyearvolume)
```

Graph that shows the volume of each different stock 
```{r}
plotvolume <- ggplot(data = fiveyearvolume, mapping = aes(x = date, y = volume, color = symbol)) +
  geom_line() +
  facet_wrap(~symbol)

plotvolume
```

Interactive graph that shows the stocks and their prices over the last 5 years 
```{r}
tickersinteractive <- tickers_today %>%
  select(symbol, date, adjusted) %>%
  pivot_wider(names_from = symbol, values_from = adjusted) %>%
  tk_xts(date_var = date)

dygraph(tickersinteractive)
```

Interactive graph that shows volume 
```{r}
tickersinteractive2 <- tickers_today %>%
  select(symbol, date, volume) %>%
  pivot_wider(names_from = symbol, values_from = volume) %>%
  tk_xts(date_var = date)

dygraph(tickersinteractive2)
```


Section 2 

Set up to build the graphs when given tickers
```{r}
tickersupdated <- tq_get(c("QQQ", "MO", "KO", "ABB", "LH", "CINF"), get = "stock.prices", from = today()-years(5), to = today())

head(tickersupdated)
```

```{r}
fiveyearadjustednew <- tickersupdated %>%
 select(symbol, date, adjusted) %>%
  pivot_wider(names_from = symbol, values_from = adjusted) %>%
  tk_xts(date_var = date)


head(fiveyearadjustednew)
```


```{r}
dygraph(fiveyearadjustednew, main = "Straw Broom Chart Percent") %>%
  dyRebase(percent = TRUE) %>%
  dyShading(from = today()-years(5), to = today()) %>%
  dyRangeSelector()
```

Graph 2
```{r}
dygraph(fiveyearadjustednew, main = "Stock Price Comparison") %>%
  dyHighlight(highlightCircleSize = 2, 
              highlightSeriesBackgroundAlpha = 0.2,
              hideOnMouseOut = FALSE) %>% 
  dyOptions(axisLineColor = "red",
            gridLineColor = "lightblue") %>% 
  dyRangeSelector(dateWindow = c(today()-years(5),today())) 
```


Set up for graph below
```{r}
fiveyearvolumenew <- tickersupdated %>%
  select(symbol, date, volume)

head(fiveyearvolumenew)
```

Graph that shows the volume of each different stock 
```{r}
plotvolumenew <- ggplot(data = fiveyearvolumenew, mapping = aes(x = date, y = volume, color = symbol)) +
  geom_line() +
  facet_wrap(~symbol)

plotvolumenew
```

Interactive graph that shows the stocks and their prices over the last 5 years 
```{r}
tickersinteractivenew <- tickersupdated %>%
  select(symbol, date, adjusted) %>%
  pivot_wider(names_from = symbol, values_from = adjusted) %>%
  tk_xts(date_var = date)

dygraph(tickersinteractivenew)
```

Interactive graph that shows volume 
```{r}
tickersinteractive2new <- tickersupdated %>%
  select(symbol, date, volume) %>%
  pivot_wider(names_from = symbol, values_from = volume) %>%
  tk_xts(date_var = date)

dygraph(tickersinteractive2new)
```


































