---
title: "Case 5"
author: "Hayden Armour"
date: "9/25/2022"
output: 
  html_document:
    keep_md: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(readr)
library(knitr)
library(tidyverse)
library(dplyr)
library(forcats)
library(downloader)
```


```{r}
download.file("https://raw.githubusercontent.com/fivethirtyeight/guns-data/master/full_data.csv", "gundata")
```

```{r}
gundata <- read.csv("gundata")

gundata
```

```{r}
agegroup <- gundata %>%
  filter(intent != "", age != "") %>%
  mutate(agegroup = 
           case_when(  
             age >= 0 & age <= 14 ~ "under 15",
             age >= 15 & age <= 34 ~ "15 - 34",
             age >= 35 & age <= 64 ~ "35 - 64",
             age >= 65 ~ "65+"),
         agegroup = fct_relevel(agegroup,
                                "under 15", "15 - 34", "35 - 64", "65+"))

agegroup
```



```{r}
plot1 <- ggplot(data = agegroup, mapping = aes(x = agegroup, fill = sex)) +
  facet_wrap(~ intent, nrow = 2, scales = 'free') +
  geom_bar() +
  scale_fill_manual(values = c("#D784B4", "#5A84D3")) +
  labs(x = 'agegroup', y = 'count', title = "Gun Deaths by Age Group")


plot1

```
Here, we can see total deaths broken down by both age, sex, and gun death type. Facet wrap made it possible to see the different types of gun deaths, and a stacked bar chart allowed us to see the difference between men and women. All of these categories show that men experience gun death at a much large rate than women do. We can also see that the 15-34 and 35-64 are overwhelmingly the categories that make up most the gun deaths, and under 15 and 65+ have the least. Suicide and homicide are the most prevelant categories. 



```{r}
plot2 <- ggplot(data = gundata, mapping = aes(x = age, fill = intent)) + 
  geom_density(position = 'fill', alpha = .5) +
  facet_wrap(~ sex) +
  labs(title = "Density of Gun Deaths by Gender")
  

plot2
```
This graph shows the density of each form of gun death; accidental, homicide, suicide, or undetermined. It is broken down by gender (facet wrapped) and it is clear that the greatest amount of gun deaths, from both men and women, falls in the homicide category. Suicide, however, for the male population, gradually becomes more promenint the more they age, and we can see that there is a clear upward trajectory for that as age increases. For women, it all forms of gun death gradually get higher until about age 65, and at that point, all forms of gun death gradually decrease. 




```{r}
gundeathsseasons <- gundata %>%
  mutate(month = as.factor(month))


gundata$month <- as.integer(gundata$month)


str(gundata)
```


```{r}
seasonaldata <- gundata %>%
  mutate(season = 
            case_when(
            month >= 1 & month <= 2 ~ "Winter",
            month == 12 ~ "Winter",
            month >= 4 & month <= 6 ~ "Spring",
            month >= 5 & month <= 8 ~ "Summer",
            month >= 9 & month <= 11 ~ "Fall",
            )
         )
seasonaldata

seasonaldata1 <- seasonaldata %>%
  filter(season != "")

seasonaldata1 

```


```{r}
plot3 <- ggplot(data = seasonaldata1, mapping = aes(x = season, color = season)) +
  geom_bar() +
  facet_wrap(~sex) +
  labs(x = 'Season Type', y = 'Total Deaths', title = 'Total Death by Season')

plot3
```
This plot shows us the total deaths broken down by sex, and by season. We can see clearly, again, that men encouter the majority of the total deaths of gun violence. For women, deaths are fairly uniform, with summer being the lowest total deaths according to season. For men, it is the same, and spring is the season that most deaths occur for me. Gun violence is worse in the colder months than it is in the warmer. 


```{r}
seasonaldata2 <- seasonaldata1 %>%
  filter(season == 'Winter')
  
seasonaldata2
```



```{r}
plot4 <- ggplot(data = seasonaldata2, mapping = aes(x = intent, fill = sex)) +
  geom_bar() +
  facet_wrap(~sex) +
  labs(x = 'Death Type', y = 'Total Deaths', title = 'Total Deaths in the Winter by Death Type') +
  scale_x_discrete(guide = guide_axis(n.dodge=3))

plot4

```
In this graph, it only includes winter data. We can see that for both men and women, suicide is the greatest threat, in the winter. Homicide is in second. It is also clear that men experience all forms at greater rates than women. 


```{r}
seasonaldata3 <- seasonaldata1 %>%
  filter(season == 'Summer')
  
seasonaldata3
```


```{r}
plot5 <- ggplot(data = seasonaldata3, mapping = aes(x = intent, fill = sex)) +
  geom_bar() +
  facet_wrap(~sex) +
  labs(x = 'Death Type', y = 'Total Deaths', title = 'Total Deaths in the Summer by Death Type') +
  scale_x_discrete(guide = guide_axis(n.dodge=3))

plot5
```
Here, we can see that men still experience much higher rates of gun death. It follows the same trend as the plot before. Suicide is the greatest risk, followed by homicide. This graph looks at the same data but for the summer. Suicide is the greatest risk in terms of gun deaths for both men and women, hot and cold. 











