---
title: "Task 10"
author: "Hayden Armour"
date: "9/27/2022"
output: 
  html_document:
    keep_md: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(ggplot2)
library(readr)
library(knitr)
library(tidyverse)
library(dplyr)
library(forcats)
library(downloader)
library(corrplot)
```


```{r}
download.file('https://raw.githubusercontent.com/martinerin/myrepo/master/financing_healthcare.csv', 'finance')
```


```{r}
finance <- read.csv('finance') 
summary(finance)
head(finance)
```


```{r}
childmort <- finance %>%
  select(year, country, child_mort) %>%
  filter(country == 'United States') %>%
  drop_na(child_mort)

childmort
```
This filtered the data to only the United States, and looked at the year and child mortality rate. I also removed NA values. 

```{r}
plot1 <- ggplot(data = childmort, mapping = aes(x = year, y = child_mort)) +
  geom_point(alpha = .2) +
  geom_line() +
  labs(x = 'Year', y = 'Child Mortality Rate', title = 'Child Mortality Rate through the Years in the United States')

plot1
```
I created a scatter plot, of which we can see that there is a downward trend, except for the spike in 1918, and that can be attributed the the influenza pandemic that occurred between 1918 and 1919. I added a trend line, and we can see that child mortality rates continue to drop as we come closer to modern time. 


```{r}
childmort1 <- finance %>%
  select(year, country, child_mort) %>%
  filter(year ==  2013, child_mort >= 7.6 & child_mort <= 20) %>%
  drop_na(child_mort)

childmort1
```
Here, I filtered the data to only include the year, country and child mortality rate in the most recent year availble, 2013, and where the child mortality rate was between the global average in 2013 (7.6%) and the global average in 1975 (20%). 



```{r}
plot2 <- ggplot(data = childmort1, mapping = aes(x = child_mort)) +
  geom_histogram(binwidth = 1.5, aes(color = 'red'), labels = TRUE) +
  labs(x = 'Child Mortality', title = 'Worldwide Child Mortality Rates', subtitle = 'For the year 2013, and where the mortality rate falls between 
the global average in 2013 (7.6%) and the global average in 1975 (20%)') 

plot2
```
I created a histogram that looks at the filtered data mentioned above. We can see that the data is very inconsistent, and follows no linear path nor a bell curve. There are spikes, and there are drops, however, we can see that a child morality rate of around 15 is the most common in the year 2013 globally. I chose red because it has to do with mortality. 















