---
title: "Case 3"
author: "Hayden Armour"
date: "9/12/2022"
output:
  html_document:
    keep_md: TRUE
---
```{r}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
#install.packages("gapminder")
#Had to comment out to get it to knit 
library(gapminder)
head(gapminder)
library(readr)
library(tidyverse)
library(knitr)
library(downloader)
library(dplyr)
```


```{r}
gapminder_edit <- filter(gapminder, country != "Kuwait")
head(gapminder_edit)
```

```{r}
ggplot(data = gapminder_edit) +
  geom_point(mapping = aes(size = pop/100000, x = lifeExp, y = gdpPercap, color = continent, group = year)) +
  facet_wrap(~ year, nrow = 1) +
  scale_y_continuous(trans = "sqrt") +
  scale_size_continuous(name = "Population (100k)") +
  xlab("Life Expectancy") +
  ylab("GDP per capita") +
  theme_bw()
```

```{r}

weighted_GDP1 <- gapminder_edit 
weighted_GDP2 <- group_by(weighted_GDP1, continent, year) 
weighted_GDP <- summarise(weighted_GDP2, weightedGDP_percap = weighted.mean(gdpPercap), Population=pop/10000)
```

```{r}
ggplot(data = gapminder_edit) +
  geom_point(aes(x = year, y = gdpPercap, color = continent)) +
  geom_line(aes(x = year, y = gdpPercap, color = continent, group = country)) +
  geom_point(data=weighted_GDP,aes(x = year, y = weightedGDP_percap, size = Population)) +
  geom_line(data=weighted_GDP,aes(x = year, y = weightedGDP_percap)) +
  facet_wrap(~ continent, nrow = 1) +
  xlab("Year") +
  ylab("GDP per capita")  
```







