---
title: "Task 20"
author: "Hayden Armour"
date: "11/15/2022"
output: 
  html_document:
    keep_md: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Recreating Case 8 

```{r}
library(knitr)
library(tidyverse)
library(downloader)
library(corrplot)
library(stringi)
library(lubridate)
library(riem)
library(gifski)
library(gganimate)
```

```{r}
tempsales <- tempfile()

download("https://github.com/WJC-Data-Science/DTS350/raw/master/sales.csv", tempsales, mode = "wb")

sales <- read_csv(tempsales)

head(sales)
```

The data are for businesses in the mountain time zone. Make sure you read in times correctly.
```{r}
salestz <- with_tz(sales, tzone = "US/Mountain")

head(salestz)

tail(salestz)
```

This is point of sale (pos) data, so you will need to use library(lubridate) to create the correct time aggregations.
```{r}

timedata <- salestz %>%
  mutate(hourofday = hour(Time)) %>%
  mutate(dayofweek = wday(Time, label = TRUE, abbr = FALSE)) %>%
  mutate(weekofyear = week(Time)) %>%
  mutate(monthofyear = month(Time)) 

tail(timedata)
```


Help your boss understand which business is the best investment through visualizations.

Provide an understanding and recommendation for hours of operation.
```{r}
hourofoperation <- timedata %>%
  group_by(Name, hourofday) %>%
  select(Name, Amount, hourofday)

head(hourofoperation)

ggplot(data = hourofoperation, mapping = aes(x = hourofday, y = Amount)) +
  geom_col() +
  labs(title = "Recommended Hours of Operation", subtitle = "Broken Down by Sales by their Respective Hours", x = "Hour of the Day", y = "Amount of Sales (+/-) in $") +
  theme(plot.title = element_text(hjust = .5)) +
  theme(plot.subtitle = element_text(hjust = .5))
```

We can see here, that the optimal hours of operation would be from 9am-8pm. There are some hour-intervals included that go below the x-axis, but it is negated by the height on the y. They ultimately make money, but incur some sort of costs along the way. 

Customer traffic is greatest between the hours of 11am and 2pm. It is virtually none between the hours of 12am and 7 am, and sees more traffic between 8am and 11pm. 



Provide a final comparison of the six companies and a final recommendation.

```{r}
ex <- hourofoperation %>% filter(Name != "Missing")
tail(ex)
```



Animated Graph
```{r}
preplot <- ggplot(data = ex, mapping = aes(x = hourofday, y = Amount, color = Name)) +
  geom_line() +
  facet_wrap(~Name) +
  labs(title = "Recomended Hours of Operation", subtitle = "Broken Down by Sales by their Respective Hours", x = "Hour of the Day", y = "Amount of Sales (+/-) in $") +
  theme(plot.title = element_text(hjust = .5)) +
  theme(plot.subtitle = element_text(hjust = .5))

preplot + transition_reveal(hourofday) 
```

Saving as gif
```{r}
anim_save('preplot.gif', animation = last_animation(), path = '/Users/hayden/Desktop/FA22 Classes/Data Visualization - Repository/DTS-350/Repository/DTS-350/Week12/Task20')
```


Animated Graph 
```{r}
preplot2 <- ggplot(data = hourofoperation, mapping = aes(x = hourofday, y = Amount)) +
  geom_col() +
  labs(title = "Recommended Hours of Operation", subtitle = "Broken Down by Sales by their Respective Hours", x = "Hour of the Day", y = "Amount of Sales (+/-) in $") +
  theme(plot.title = element_text(hjust = .5)) +
  theme(plot.subtitle = element_text(hjust = .5))

preplot2
head(hourofoperation)

preplot2 + transition_states(hourofday, transition_length = 2, state_length = 1) + shadow_mark() + ease_aes('sine-in-out') 
```

Saving as gif
```{r}
anim_save('preplot2.gif', animation = last_animation(), path = '/Users/hayden/Desktop/FA22 Classes/Data Visualization - Repository/DTS-350/Repository/DTS-350/Week12/Task20')
```


