---
title: "Case 11"
author: "Hayden Armour"
date: "11/14/2022"
output: 
  html_document:
    keep_md: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in libraries 
```{r}
library(ggplot2)
library(readr)
library(knitr)
library(tidyverse)
library(dplyr)
library(forcats)
library(downloader)
library(corrplot)
library(tidyquant)
library(stringr)
library(plotly)
library(gridExtra)
library(USAboundaries)
library(sf)
library(leaflet)
```


Read in the permits data
```{r}
permits <- read_csv("https://github.com/WJC-Data-Science/DTS350/raw/master/permits.csv")

head(permits)
```

Filter to just PA data from 2010
```{r}
permitsPA <- permits %>%
  filter(StateAbbr == "PA", year == 2010)

head(permitsPA)
```

Read in the data to combine 
```{r}
latlong <- read_csv("latlong.csv")

head(latlong)
```

Create new column so that it is named 'county' and it is a character
```{r}
latlong1 <- latlong %>%
  mutate(countyname1 = as.character(`County Name`))

head(latlong1)
```

Change the county column to type character 
```{r}
permitsPA1 <- permitsPA %>%
  mutate(countyname = as.character(countyname))

head(permitsPA1)

permitsPA2 <- permitsPA1 %>%
  mutate(countyname1 = str_sub(countyname, end = -8))

  
str(permitsPA2)
str(latlong1)
```


```{r}
combined <- left_join(latlong1, permitsPA2, by = 'countyname1')

head(combined)
```

```{r}
combined1 <- combined %>%
  arrange(desc(value)) %>%
  mutate(value = as.character(value))
  
  

head(combined1)
```

Get the county with the largest value (largest permits awarded/used)
```{r}
topcounty <- combined1 %>%
  filter(row_number() == 1)

topcounty
```


Get the counties for PA and create a state map of PA 
```{r}
PA <- us_counties(states = 'PA')

PAcounties <- ggplot(PA) +
  geom_sf()

PAcounties
```


Finding the top 25%, top 25-50%, bottom 25-50% and bottom 25% 

```{r}
combined1$quartile <- ntile(combined1$value, 4)

combined1

ntile4 <- combined1 %>%
  filter(quartile == 4)

ntile4

ntile3 <- combined1 %>%
  filter(quartile == 3)

ntile3

ntile2 <- combined1 %>%
  filter(quartile == 2)

ntile2

ntile1 <- combined1 %>%
  filter(quartile == 1)

ntile1
```

Quartile 4 is top 25%
Quartile 3 is top 25-50%
Quartile 2 is bottom 25-50%
Quartile 1 is bottom 25% 

```{r}

leaflet(combined1) %>%
  addTiles() %>%
  addCircleMarkers(data = ntile4, radius = 7, color = 'orange', stroke = FALSE, fillOpacity = 1, popup = ~value) %>%
  addCircleMarkers(data = ntile3, radius = 7, color = 'darkgreen', stroke = FALSE, fillOpacity = 1, popup = ~value) %>%
  addCircleMarkers(data = ntile2, radius = 7, color = 'firebrick', stroke = FALSE, fillOpacity = 1, popup = ~value) %>%
  addCircleMarkers(data = ntile1, radius = 7, color = 'yellow', stroke = FALSE, fillOpacity = 1, popup = ~value) %>%
  addCircleMarkers(data = topcounty, radius = 7, color = 'hotpink', stroke = FALSE, fillOpacity = 1, popup = ~value) 
```




