---
title: "Task 5"
author: "Hayden Armour"
date: "9/4/2022"
output:
  html_document:
    keep_md: TRUE
    code_folding: 'hide'
---

```{r}
library(tidyverse)
library(knitr)
library(downloader)
```


All data imported correctly as characters. All data imported was of charachter type
```{r}
SoloData <- read_csv("solo-artist-followers.csv")
SoloData
str(SoloData)
```


Data imported correctly - date type for date, charachter for titles, names, and bands. 
```{r}
BillboardData <- read_csv("billboard-hits.csv")
str(BillboardData)
head(BillboardData)
```

In BillboardData remove all singers who do not have at least 6 times they had a top 100 hit.
```{r}
sixtop100 <- BillboardData %>%
  group_by(name) %>%
  filter(n() > 6, band != "", !is.na(band))
head(sixtop100)
```
Left me with 144 entries 

```{r}
sixtopbands <- BillboardData %>%
  group_by(band) %>%
  filter(band %in% sixtop100$band)
head(sixtopbands)
```

```{r}
ggplot(data = sixtop100, aes(x = peak_date, y = peak_rank, color = name, group = name)) +
  geom_point() +
  geom_line() +
  geom_point(data = sixtopbands, color ="black") +
  geom_line(data = sixtopbands, color = "black", linetype = "dotted") +
  facet_wrap(~ band, scales = "free") +
  xlab("peak_date") + ylab("peak_rank") +
  theme_bw() 
```
Observations made:
One Direction artists had different paths to success. ZAYN was mostly upwards while Harry Styles was all over the place
None saw linear success - NSYNC had a lot of hits compared to Destiny's Child who had both lots of top 10 hits and lots of hits over 50 ranking
None see prolonged success in terms of ranking - almost none have multiple songs back to back to back
Destiny's Child had the most top 100 hits 
Aventura had the least amount of top 100 hits. 


https://www.kaggle.com/datasets/migeruj/videogames-predictive-model
Info: includes platform, genre, publisher, North American sales, Europe sales, Japan sales, other sales, global sales, and rating
```{r}
videogames <- read_csv("videogamesales.csv")
videogames
str(videogames)
```
Are data types correct? 
Yes - all character values 

https://www.kaggle.com/datasets/dtrade84/us-state-life-expectancy-by-sex-2020
Info: Life expecatnacy data broken down by state. Looks at different genders as well. 
```{r}
lifeexpectancy <- read_csv("life-expectancy.csv")
lifeexpectancy
str(lifeexpectancy)
```
Are the data types correct? 
Yes - character values for what is needed (sex), and number values for where they are needed (life expectancy)


https://github.com/owid/covid-19-data/tree/master/public/data
Info: Covid data that includes location, date, total cases, new cases, reporduction, icu patients, hospital admissions and more
```{r}
coviddata <- read_csv("owid-covid-data.csv")
coviddata
str(coviddata)
```
Are the data types correct? 
Yes. All numbers are labeled correctly, all words are labeled correctly 



