---
title: "Case 4"
author: "Hayden Armour"
date: "9/18/2022"
output: 
  html_document:
    keep_md: TRUE
    code_folding:  'hide'
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(ggplot2)
library(readr)
library(knitr)
library(tidyverse)
library(dplyr)
library(forcats)
library(downloader)

#install.packages("nycflights13")
library(nycflights13)
```


```{r}
flights
```

SECTION 1 

If I am leaving before noon, which two airlines do you recommend at each airport (JFK, LGA, EWR) that will have the lowest delay time at the 75th percentile?

Only JFK data 
```{r}
jfkdata <- flights %>%
  filter(origin == "JFK")

jfkdata
```

```{r}
jfkavg <- jfkdata %>%
  filter(dep_delay >= 0) %>%
  summarise(avgdelay = mean(dep_delay))

jfkavg
```

Filtered JFK Data
```{r}
jfkavg <- jfkdata %>%
  group_by(carrier) %>%
  filter(dep_delay >= 0) %>%
  summarise(avgdelay = mean(dep_delay))

jfkavg
```

JFK Graph
```{r}
jfkgraph <- ggplot(data = jfkavg, mapping = aes(x = carrier, y = avgdelay, color = carrier)) +
  geom_point() 

jfkgraph

airlines
  
```
At JFK, the airlines with the two highest departure delays are EV (ExpressJet Airlines Inc.) and 9E (Endeavor Air Inc.)

The airlines with the two lowest average departure delays are US (US Airways Inc.) and DL (Delta Air Lines Inc.)



Only LGA data 
```{r}
lgadata <- flights %>%
  filter(origin == "LGA")

lgadata

```


Filtered LGA Data
```{r}
lgaavg <- lgadata %>%
  group_by(carrier) %>%
  filter(dep_delay >= 0) %>%
  summarise(avgdelay = mean(dep_delay))

lgaavg
```


LGA Graph
```{r}
lgagraph <- ggplot(data = lgaavg, mapping = aes(x = carrier, y = avgdelay, color = carrier)) +
  geom_point() 

lgagraph
```
At LGA, the airlines with the two highest departure delays are EV (ExpressJet Airlines Inc.) and OO (Skywest Airlines Inc.)

The airlines with the two lowest average departure delays are WN (Southwest Airlines Co.) and US (Us Airways Inc.)


Only EWR data 
```{r}
ewrdata <- flights %>%
  filter(origin == "EWR")

ewrdata
```

Filtered EWR Data
```{r}
ewravg <- ewrdata %>%
  group_by(carrier) %>%
  filter(dep_delay >= 0) %>%
  summarise(avgdelay = mean(dep_delay))

ewravg
```



```{r}
ewrgraph <- ggplot(data = ewravg, mapping = aes(x = carrier, y = avgdelay, color = carrier)) +
  geom_point() 

ewrgraph
```
At EWR, the airlines with the two highest departure delays are OO (SkyWest Airlines Inc.) and EV (ExpressJet Airlines Inc.)

The airlines with the two lowest average departure delays are UA (United Air Lines Inc.) and AS (Alaska Airlines Inc.)



SECTION 2 


Which origin airport is best to minimize my chances of a late arrival when I am using Delta Airlines?
```{r}

avgorigindelay <- flights %>%
  group_by(origin) %>%
  filter(arr_delay >= 0, carrier == "DL") %>%
  summarise(avgdelay = mean(arr_delay))

avgorigindelay
```


```{r}
delayplot <- ggplot(data = avgorigindelay, mapping = aes(x = origin, y = avgdelay, fill = origin)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Origin Airport", y = "Average Delay Time", title = "Average Delay Times of Delta Airline Planes", subtitle = "Early Arrivals Excluded")

delayplot
```
When using Delta Airlines, coming out of JFK provides the best chances, on average, to avoid a late arrival. 


